% http://www.latextemplates.com/template/classicthesis-styled-cv
% documentclass {{{
\documentclass{scrartcl}
% }}}
% Packages {{{
\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage{hyperref} % Required for adding links and customizing them
\usepackage{xcolor} % colors
\usepackage{microtype}
% }}}
% Package configuration {{{
\reversemarginpar% Move the margin to the left of the page 
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors
\newlength{\datebox}\settowidth{\datebox}{2008--Present} % Set the width of the date box in each block
% }}}
% Macros {{{
% margin text
% #1 text to go in margin
\newcommand{\MarginText}[1]{\marginpar{\scshape\small #1}}

% contact info
% #1 contact method
% #2 contact data
\newcommand{\NewContact}[2]{\noindent\hangindent=2em\hangafter=0
                            \parbox{\datebox}{\textit{#1}}
                            \hspace{1.5em} #2}

% Entry command
% #1 date field 
% #2 position title 
% #3 description
\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 
                          \parbox{\datebox}{\small \textit{#1}}
                          \hspace{1.5em} \textcolor{Maroon}{#2} 
                          #3 \vspace{0.5em}}

% description of position
% #1 description
% #2 location
\newcommand{\Description}[2]{\hangindent=2em\hangafter=0\noindent
                             \footnotesize{#1}\newline
                             \textcolor[HTML]{5C6983}{\textup{#2}}
                             \par\normalsize\vspace{1em}}

% invited talk
% #1 description
% #2 location
\newcommand{\Talk}[3]{\noindent\hangindent=2em\hangafter=0 
                      \textit{#1}\newline
                      #2\newline
                      \textcolor[HTML]{5C6983}{#3} \vspace{0.5em}}

% skills
% #1 list of skills
\newcommand{\Skills}[1]{\hangindent=2em\hangafter=0\noindent
                        \footnotesize{#1}
                        \par\normalsize\vspace{1em}}

\begin{document}

\pagenumbering{gobble} % remove all page numbers

% }}}
% Name and contact information {{{

\begin{cv}{\spacedallcaps{Jacob Carey}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewContact{email}{\href{mailto:jacobcvt12@gmail.com}{jacobcvt12@gmail.com}} \\ % Email address
\NewContact{github}{\href{https://github.com/jacobcvt12}{https://github.com/jacobcvt12}} \\ % github
\NewContact{phone}{{\fontfamily{cmr}\selectfont +1 (434) 203-9317}} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal
% }}}
% Education {{{
\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2014--2016}{Master of Science}

\Description{\MarginText{Johns Hopkins University}\textbf{Epidemiology}\ \ $\cdotp$\ \ Bloomberg School of Public Health\newline 
Thesis: \textit{Characterizing Risk of Transmission of Respiratory Viruses among School Children using Proxies of Infectious Contact and Genetic Data}\newline
Advisor: Dr. Derek Cummings}{Baltimore, MD}

%------------------------------------------------

\NewEntry{2008--2012}{Bachelor of Science}

\Description{\MarginText{Virginia Tech}\textbf{Mathematics}\ \ $\cdotp$\ \ College of Science}{Blacksburg, VA}

%------------------------------------------------

\vspace{1em} % Extra space between major sections
% }}}
% Professional experience {{{
\noindent\spacedlowsmallcaps{Professional Experience}\vspace{1em}

\NewEntry{2017--Present}{Senior Biostatistician}

\NewEntry{2016--2017}{Biostatistician}

\Description{\MarginText{Telligen}Create nonlinear model for predicting number of hospital acquired infections within facilities. Develop hierarchical models to analyze quality of care factors. Create interactive dashboard to communicate key results to clients.}{Columbia, MD}

%------------------------------------------------

\NewEntry{2014}{Data Scientist}

\Description{\MarginText{Marriott}Assisted with new Marriott user-centric sort order algorithm. Developed time series model to determine effectiveness of hotel promotions. Calculated weekly values of search engine keywords in order to best allocate online marketing funds. Performed web scraping of external websites to provide business insights. Worked with datasets greater than one billion rows. Automated reports using R \& ggplot2 and ETL using Python scripts.}{Bethesda, MD}

%------------------------------------------------

\NewEntry{2012--2014}{Data Analyst}

\Description{\MarginText{Deloitte}Managed a client-facing team of three consultants in the analysis of datasets greater than one million rows. Led regular meetings and presented results and data visualizations to key clients and internal stakeholders. Developed web application to be used by federal agencies to optimize resource allocation. Assisted federal agency in meeting requirements of government act using sample selection and estimation of disbursed grants and transactions.}{Arlington, VA}

%------------------------------------------------

\vspace{1em} % Extra space between major sections
% }}}
% Research Experience {{{
\noindent\spacedlowsmallcaps{Research Experience}\vspace{1em}

\NewEntry{2016--Present}{Division of Biostatistics \& Bioinformatics}

    \Description{\MarginText{Johns Hopkins University}Extend non-negative matrix factorization software to semi-supervised algorithm for time course data. Work on extending current Gibbs Sampling algorithm to scalable Variational Inference algorithm. Software can be found at\newline\href{https://www.bioconductor.org/packages/CoGAPS/}{www.bioconductor.org/packages/CoGAPS/}\newline Supervisor: Dr. Elana Fertig}{Baltimore, MD}

\NewEntry{2015}{Division of Biostatistics \& Bioinformatics}

\Description{\MarginText{Johns Hopkins University}Developed R package for Bayesian mixture models implemented in C++. Package developed infers DNA copy number in genomic studies. Software can be found at\newline\href{https://www.bioconductor.org/packages/CNPBayes/}{www.bioconductor.org/packages/CNPBayes/}\newline Supervisor: Dr. Robert Scharpf}{Baltimore, MD}
% }}}
% Invited Talks {{{
\noindent\spacedlowsmallcaps{Invited Talks}\vspace{1em}

\Talk{Introduction to Variational Inference}{Bayesian Methods - Johns Hopkins University}{Baltimore, MD. March 2017}

\vspace{1em} % Extra space between major sections
% }}}
% Skills {{{
\noindent\spacedlowsmallcaps{Skills}\vspace{1em}

\Skills{\MarginText{Programming}R\ \ $\cdotp$\ \ JAGS\ \ $\cdotp$\ \  Stan \ \ $\cdotp$\ \  Julia \ \ $\cdotp$\ \ C++\ \ $\cdotp$\ \  Python\ \ $\cdotp$\ \  SQL\ \ $\cdotp$\ \ git\ \ $\cdotp$\ \  Vim\ \ $\cdotp$\ \  Bash\ \ $\cdotp$\ \ \LaTeX}

\Skills{\MarginText{Statistics}Statistical computing\ \ $\cdotp$\ \ Bayesian statistics\ \ $\cdotp$\ \ Multilevel modeling\ \ $\cdotp$\ \ Machine learning\ \ $\cdotp$\ \ Regression analysis\ \ $\cdotp$\ \ Time series analysis\ \ $\cdotp$\ \ Data visualization\ \ $\cdotp$\ \ Web scraping}

\Skills{\MarginText{Environments}OS X\ \ $\cdotp$\ \ Debian\ \ $\cdotp$\ \ Ubuntu\ \ $\cdotp$\ \ Red Hat/CentOS}

\vspace{1em} % Extra space between major sections
% }}}
% Articles {{{
\noindent\spacedlowsmallcaps{Articles}\vspace{1em}
\vspace{1em} % Extra space between major sections
% }}}
% Ending {{{
\end{cv}
\end{document}
% }}}
% vim:foldmethod=marker:foldlevel=0
